Precise predictions for same-sign W-boson scattering at the LHC

### 2018-02-21 Draft/definition.tex
minor changes on definition.tex

\begin{figure*}[t]
\begin{center}
          \includegraphics[width=0.30\linewidth]{feynman/LO_EW_5}
          \raisebox{.5ex}{\includegraphics[width=0.35\linewidth]{feynman/LO_EW_2}}
          \raisebox{-1.8ex}{\includegraphics[width=0.32\linewidth]{feynman/LO_EW_3}}
\end{center}
        \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
        In addition to typical VBS contribution (left), this order also possesses $s$-channel contributions such as decay chain (middle) and tri-boson contributions (right).}
\label{diag:LO}
\end{figure*}

@@

This process possesses three LO contributions of different orders.
At LO, this process can proceed via three different coupling-order combinations:
$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
The first, commonly referred to as EW contribution or VBS~\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
of vector bosons}, receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
(center diagram) or from
triple-boson production (right diagram).
Note that $s$-, $t$-, and $u$-channel contributions are defined according to the quark lines.
$s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line.
$u$-channel refers to contributions with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state
The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.

@@

The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
radiated off the quark lines. Because of the different colour structure, this contribution features
different kinematical behaviours than VBS. Nonetheless they share the same final state and therefore constitute an irreducible background.

Finally, the third contribution is the interference of the two type of amplitudes described above.
It is non-zero only for those partonic subprocesses which involve only one quark family.
Such a contribution is typically small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.

>>>>

\begin{figure*}[t]
\begin{center}
          \includegraphics[width=0.30\linewidth]{feynman/LO_EW_5}
          \raisebox{.5ex}{\includegraphics[width=0.35\linewidth]{feynman/LO_EW_2}}
          \raisebox{-1.8ex}{\includegraphics[width=0.32\linewidth]{feynman/LO_EW_3}}
\end{center}
        \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
        In addition to typical VBS contributions (left), this order also possesses $s$-channel contributions such as decay chain (middle) and tri-boson contributions (right).}
\label{diag:LO}
\end{figure*}

@@

This process possesses three LO contributions of different orders.
At LO, this process can proceed via three different coupling-order combinations:
$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
The first, commonly referred to as EW contribution or VBS~\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
of vector bosons.}, receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
(center diagram) or from
triple-boson production (right diagram).
Note that $s$-, $t$-, and $u$-channel contributions are defined according to the quark lines.
$s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line.
$u$-channel refers to contributions with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state
The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.

@@

The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
radiated off the quark lines. Because of the different colour structure, this contribution features a 
different kinematical behaviour than VBS. Nonetheless they share the same final state, and this class of contributions therefore constitutes an irreducible background to the genuine VBS signal.

Finally, the third contribution is the interference of the two types of amplitudes described above.
It is non-zero only for those partonic subprocesses which involve only one quark family.
Such a contribution is typically small but not negligible for realistic experimental set-ups \cite{Biedermann:2017bss}.
